### 2020-07-14 Model Data Sheets and Code/Zaca MCF Mortality Model Results.Rmd
minor change

c <- partialPlot(rfm, as.data.frame(mcf), slope, "Low") 
d <- partialPlot(rfm, as.data.frame(mcf), slope, "Moderate") 
b <- partialPlot(rfm, as.data.frame(mcf), slope, "High", col="red", ylim=c(-0.8,0.8))

@@

>>>>

c <- partialPlot(rfm, as.data.frame(mcf), slope, "Low") 
d <- partialPlot(rfm, as.data.frame(mcf), slope, "Moderate") 
b <- partialPlot(rfm, as.data.frame(mcf), slope, "High", col="red", ylim=c(-0.8,0.8))
lines(c, col="green")

@@

c <- partialPlot(rfm, as.data.frame(mcf), slope, "Other") 
b <- partialPlot(rfm, as.data.frame(mcf), slope, "High", col="red", ylim=c(-0.8,0.8)) 
lines(c, col="green")
